%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\usepackage{ifthen}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \ifthenelse{\equal{#1}{}}
    {
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
    }
    {
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
    }
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Jin Fan} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:14168581488}{(416) 858-1488}
    $|$
    \faAt \hspace{.5pt} \href{mailto:jingyangfan16@gmail.com}{jingyangfan16@gmail.com}
    $|$
    % \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/jingyangfan}{LinkedIn}
    % $|$
    \faGithub \hspace{.5pt} \href{https://github.com/Jay2theWhy}{Jay2theWhy}
\end{center}


%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {Western University
      }{Ontario, Canada}
      {Masters in Data Analytics}{2019 \textbf{--} 2020}
      {B.M.Sc in Biochemistry of Infection and Immunity}{2015 \textbf{--} 2019}

  \resumeSubHeadingListEnd


%----------- WORK EXPERIENCE -----------

\section{Work Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Laserfiche}{Toronto, Ontario}
      {Software Engineer \textbf{--} Product Engineering Team}{2022 \textbf{--} Present, Full-time}
        \resumeItemListStart
            \resumeItem{Led the migration of our \textbf{AWS EC2} containers to \textbf{AWS EKS} using \textbf{Kubernetes} to improve scalability while reducing costs. Monthly AWS expenditure was reduced by a 5-figure dollar value and no outages have occurred to date.}
            \resumeItem{Took ownership of two \textbf{C\#} microservices and improved the performance of client-facing actions when run against a large number of users (10,000 to 30,000). \textbf{Reduced latency for users by 93\%} by utilizing bulk database reads and writes to minimize time-intensive operations.}
            % \resumeItem{Initiated and executed a project to add automated test coverage reporting for all \textbf{azure YAML build pipelines}. These reports identified that \textbf{4 out of 9 projects} were lacking sufficient integration testing, resulting in a move to add and update test cases for these projects.}
            \resumeItem{Created \textbf{REST API} endpoints using \textbf{Typescript} and \textbf{C\#} to serve client requests on our account control system. Rigorous unit, functionality, and webapi tests were used for monitoring the endpoints, and they currently have a success rate of \textbf{98\% over the last 6 months}.}
            \resumeItem{Initiated and executed a project to overhaul all user dialogues in our client-facing application using \textbf{Angular} and \textbf{Typescript}. Resulted in reusable and extensible components that improved the developer experience, which lead to the creation of user stories to refactor other front-end components in the same manner.}
            \resumeItem{Identified performance bottlenecks in our services using \textbf{Kibana} logs and \textbf{Grafana} dashboards after observing unexplained spikes in CPU and Memory usage in the Test environment. Findings were presented to the team, and was tasked with resolving the bottlenecks which resulted in a \textbf{60\% reduction in memory leaks}.}
        \resumeItemListEnd

    \resumeSubheading
      {}{}
      {Software Engineer \textbf{--} Product Intelligence Team}{}
        \resumeItemListStart
            \resumeItem{Developed and maintained \textbf{AWS Lambda} ETL functions to monitor product usage, capture events in \textbf{DynamoDB}, process data, and store data in \textbf{Redshift}. Designed architecture with reliability in mind, incorporating fallback strategies for failed events and enabling real-time error alerts across environments.}
            % \resumeItem{Led the creation of robust \textbf{CI/CD pipelines}, enabling automated building and deployment of projects. Utilized multi-stage deployment and rollback strategies to ensure seamless production updates without disruptions. Pipelines currently have a \textbf{success rate of 96\%} over the last 6 months, an improvement over the old pipelines by \textbf{\~25\%}.}
            \resumeItem{Designed and implemented a user feedback feature for our flagship platform, enabling attachment of image and GIF files. Leveraged \textbf{AWS Redshift} for data storage, with a fail-safe mechanism for capturing failed instances in an \textbf{S3 bucket} for future reprocessing. Feature had a \textbf{success rate of 100\%} over the last 6 months with no feedback messages lost.}
            \resumeItem{Created internal web applications using \textbf{Angular} and \textbf{Flask}, enabling non-technical users to track their events in Redshift via drop-down menus. Managed the deployment within \textbf{Docker} containers, leveraging \textbf{Nginx} as the reverse proxy for efficient application delivery.}
        \resumeItemListEnd


    \resumeSubheading
      {City of Toronto}{Toronto, Ontario}
      {Software Developer}{2021 \textbf{--} 2022, Full-time}
        \resumeItemListStart
            \resumeItem{Developed and implemented \textbf{Python} scripts to automate the quarterly extraction of recreation program performance metrics, transitioning away from manual SQL queries. This automation reduced human error and decreased analysis times by \textbf{90\%}.}
            \resumeItem{Engineered and maintained analytical visualization dashboards using \textbf{Plotly}, leading the project from conception to deployment. Optimized data accessibility and significantly minimized ad-hoc data requests by \textbf{over 80\%}.}
            \resumeItem{Collaborated with city planners, managers, and directors to advocate for the integration of analytical dashboards, enhancing data-driven decision-making across departments. This initiative led to \textbf{division-wide adoption of dashboards}.}
            \resumeItem{Led a project analyzing cell phone usage data with \textbf{Python} to monitor changes in park visitation patterns during the COVID-19 pandemic. My findings informed division directors, driving actionable insights for park maintenance improvements.}
        \resumeItemListEnd
    
    \resumeSubheading
      {Doxim Solutions}{Markham, Ontario}
      {Software Developer}{2020, Internship}
        \resumeItemListStart
            \resumeItem{Developed pattern recognition software, streamlining the conversion process of legacy \textbf{PowerShell scripts} into concise and reusable \textbf{C\# components}. This significantly reduced manual effort, enhanced code maintainability, and promoted codebase modernization.}
            \resumeItem{Extracted, transformed, and analyzed credit union user data from internal databases using \textbf{SQL} queries. The insights derived from this analysis contributed to strategic decision-making processes.}
            \resumeItem{Spearheaded the design and implementation of a dynamic \textbf{C\# data pipeline}, facilitating seamless integration with a third-party database. This initiative improved the usability reliability, and performance of internal data flow.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd


%----------- PROJECTS -----------

% \section{Projects}
%     \vspace{3pt}
%     \resumeSubHeadingListStart
      
%       \resumeProjectHeading
%         {\textbf{Cryptocurrency Dashboard}}{}
%           \resumeItemListStart
%             \resumeItem{Created a \textbf{React} dashboard application to
%             display comprehensive information about different cryptocurrencies}
%             \resumeItem{Fetched cryptocurrency data from a \textbf{REST}
%             endpoint using \textbf{Redux toolkit}. Data included historical
%             pricing, daily volume, news articles, exchanges, and more}
%             \resumeItem{Application was made to be compatible on both mobile
%             devices and desktop computers with varying display sizes. Utilized
%             design components from \textbf{Ant Design} to achieve modernized
%             look and feel}
%           \resumeItemListEnd
      
%       \resumeProjectHeading
%         {\textbf{Generating Game Data Using REST API}}{}
%           \resumeItemListStart
%             \resumeItem{Built \textbf{Python application} to auto-generate
%             rating reports for board games, by obtaining reviews and statistics
%             from BoardGameGeek's API and feeding the data through a
%             \textbf{Natural Language Processing} model}
%             \resumeItem{Utilized application to identify common trends and key
%             qualities in board game popularity}
%           \resumeItemListEnd
      
%     \resumeSubHeadingListEnd


%----------- SKILLS -----------

\section{Technical Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Programming Languages:}{ Python, Javascript, Typescript, C\#, SQL, C, Bash, PowerShell} \\ \vspace{3pt}
        \textbf{Frameworks:}{ React, RxJS, Angular, Entity Framework, Vue, Express, Flask} \\ \vspace{3pt}
        \textbf{Tools \& Technologies:}{ AWS, Node, Kubernetes, Docker, Nginx, Kibana, Grafana, ElasticSearch} \\
    }}
  \resumeSubHeadingListEnd


%----------- CERTIFICATES -----------

% \section{Certificates}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Procter \& Gamble VIA Certificate Program}{Feb 2022}{Business Skills, Data and Digital Skills, Project Management and Personal Productivity}
    
  % \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
